---
title: "Cash Flow Analysis"
author: "Act. Bernardo Mondragon Brozon"
date: "January 16, 2019"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
# Load libraries
library(lubridate)
library(ggplot2)
library(latex2exp)
# Avoid scientific notation
options(scipen = 999)
```

```{r economical assumptions}
t <- 5 # Lifetime of the company
# Mexican economy
y <- 0.10 # Annual interest rate
r <- -0.02 # Inflation rate
```

\section{Assumptions}

The cash flow analysis will consist of computing the present value of the future revenue of all projects that the company will generate in the following $`r t`$ years making the following assumptions:

\begin{itemize}
\item Risk free annual effective interest rate of Mexican economy: `r y`.
\item Sustained price annual increment ratio of technology: `r r`.
\end{itemize}

The company will work on $5$ types of projects at the same time:

\begin{enumerate}
\item Landing pages (only images, company description, contact, almost no functionality),
\item Small projects (basic functionality, manage users, blog, order, e-comerce),
\item Large projects (adding complex functionality, complex back-end computations),
\item Enterprice projects (thousands of users, complex back-end operations), and
\item Inhouse projects (EVA like projects).
\end{enumerate}

Each type of project will arrive to the company according to a Poisson point process with a given ratio $\lambda$ per year. In other words, the company will arrange contracts with frequency in such a way that it will have development start points randomly distributed in the timeline with a given average. For example, we will consider that the company will develop an average of $\lambda=24$ landing pages in a year (two each month). We will make these kind of assumptions for each type of project the company wants to develop and the average of contracts in a year will depend on the size of the project. 

```{r, code=readLines("discounted-cash-flows.R")}
```

\section{Landing pages}

```{r landing pages}
# Project
projectType="01Landings" # Project type
averagePrice=10000 # Expected price of the project
sdPrice=2000 # Standar deviation of the price of the project
lambda=12*2 # Expected number of projects developed in a year
# Development time distribution
sop=c(1, 2, 3)
probs=c(4/6, 1/6, 1/6)
# Payment scheme
advanceFeeRate=1 # Percentage of the final price that is paid at the begining of the project
monthlyFeeRate=0 # Percentage of the final price that is paid during the development of the project
finalFeeRate=0 # Percentage of the final price that is paid at the end of the development of the project
monthlyRentRate=0.025 # Percentaje of the price of the project to be charged monthly for project maintenance

valueLandings <- getProjectsCashFlows(
  t,
  # Mexican economy
  y, # Annual interest rate
  r, # Inflation rate
  # Project
  projectType, # Project type
  averagePrice, # Expected price of the project
  sdPrice, # Standar deviation of the price of the project
  lambda, # Expected number of projects developed in a year
  # Development time distribution
  sop,
  probs,
  # Payment scheme
  advanceFeeRate, # Percentage of the final price that is paid at the begining of the project
  monthlyFeeRate, # Percentage of the final price that is paid during the development of the project
  finalFeeRate, # Percentage of the final price that is paid at the end of the development of the project
  monthlyRentRate # Percentaje of the price of the project to be charged monthly for project maintenance
)
```

These type of projects will arrive to the company with a ratio of $`r lambda`$ per year and will consider the following assumptions:

\begin{itemize}
\item The price of the project will be $\$`r averagePrice`$ MXN in average with a standar deviation of $\$`r sdPrice`$ MXN and will have the following distribution:

```{r landings price distribution, fig.align="center", fig.width=4, fig.height=2}
ggplot(data.frame(x = c(0, 2 * averagePrice)), aes(x = x)) + 
  stat_function(fun = dlnorm, args = list(mean = log(averagePrice), sd = 1 / log(sdPrice))) +
  ggtitle("Price density function") +
  labs(x = TeX('$x$'), y = TeX('$f_{Price}(x)$')) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = averagePrice)
```

The vertical line in the graph above represents the average price of the project. 

\item The development time meaured in montsh of the project will have the following discrete distribution:

```{r landings time distribution, fig.align = "center", fig.width=4, fig.height=2}
vals <- c()
for (i in 1:10000) {
  val <- sampleFromMonthsDistribution(sop = sop, probs = probs)
  vals <- c(vals, val)
}
ggplot(data.frame(vals), aes(x=vals)) + 
  geom_histogram(aes(y = ..count../sum(..count..)), color="black", fill="white") +
  geom_vline(xintercept = mean(vals)) +
  ggtitle("Months probability law") +
  labs(x = TeX('$m (month)$'), y = TeX('$Pr(M=m)$')) +
  theme(plot.title = element_text(hjust = 0.5))
```

The vertical line in the graph above represents the average development time of the project measured in months. 

\item $`r advanceFeeRate`\times 100$ percent of the project will be charged in advance.
\end{itemize}

The positive cash flows that the company will obtain during the following $`r t`$ years due to the development of these type of projects will look similar to the following graph:

```{r landings cash flows graph, fig.align = "center"}
valueLandings$Revenues
```

Project arrivals to the company will look like the following graph:

```{r landings arrivals graph, fig.align = "center", fig.width = 7, fig.asp = 0.2}
valueLandings$Arrivals
landigsProjectsValue <- valueLandings$`Projects PV`
```

Given the previous future cash flows, the present value of the revenues of these projects is worth $\$`r landigsProjectsValue`$ MXN.

\section{Small projects}

```{r small projects}
# Project
projectType="02SmallProjects" # Project type
averagePrice=50000 # Expected price of the project
sdPrice=20000 # Standar deviation of the price of the project
lambda=5 # Expected number of projects developed in a year
# Development time distribution
sop=c(   2,   3,    4,    5,   6,   7,   8)
probs=c(2/37,4/37,15/37,10/37,3/37,2/37,1/37)
# Payment scheme
advanceFeeRate=0.25 # Percentage of the final price that is paid at the begining of the project
monthlyFeeRate=0.5 # Percentage of the final price that is paid during the development of the project
finalFeeRate=0.25 # Percentage of the final price that is paid at the end of the development of the project
monthlyRentRate=0.05 # Percentaje of the price of the project to be charged monthly for project maintenance

valueSmallProjects <- getProjectsCashFlows(
  t,
  # Mexican economy
  y, # Annual interest rate
  r, # Inflation rate
  # Project
  projectType, # Project type
  averagePrice, # Expected price of the project
  sdPrice, # Standar deviation of the price of the project
  lambda, # Expected number of projects developed in a year
  # Development time distribution
  sop,
  probs,
  # Payment scheme
  advanceFeeRate, # Percentage of the final price that is paid at the begining of the project
  monthlyFeeRate, # Percentage of the final price that is paid during the development of the project
  finalFeeRate, # Percentage of the final price that is paid at the end of the development of the project
  monthlyRentRate # Percentaje of the price of the project to be charged monthly for project maintenance
)
```

These type of projects will arrive to the company with a ratio of $`r lambda`$ per year and will consider the following assumptions:

\begin{itemize}
\item The price of the project will be $\$`r averagePrice`$ MXN in average with a standar deviation of $\$`r sdPrice`$ MXN and will have the following distribution:

```{r small projects price distribution, fig.align="center", fig.width=4, fig.height=2}
ggplot(data.frame(x = c(0, 2 * averagePrice)), aes(x = x)) + 
  stat_function(fun = dlnorm, args = list(mean = log(averagePrice), sd = 1 / log(sdPrice))) +
  ggtitle("Price density function") +
  labs(x = TeX('$x$'), y = TeX('$f_{Price}(x)$')) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = averagePrice)
```

The vertical line in the graph above represents the average price of the project. 

\item The development time meaured in montsh will have the following discrete distribution:

```{r small projects time distribution, fig.align = "center", fig.width=4, fig.height=2}
vals <- c()
for (i in 1:10000) {
  val <- sampleFromMonthsDistribution(sop = sop, probs = probs)
  vals <- c(vals, val)
}
ggplot(data.frame(vals), aes(x=vals)) + 
  geom_histogram(aes(y = ..count../sum(..count..)), color="black", fill="white") +
  geom_vline(xintercept = mean(vals)) +
  ggtitle("Months probability law") +
  labs(x = TeX('$m (month)$'), y = TeX('$Pr(M=m)$')) +
  theme(plot.title = element_text(hjust = 0.5))
```

The vertical line in the graph above represents the average development time of the project measured in months. 

\item $`r advanceFeeRate`\times 100$ percent of the project will be charged in advance.
\item $`r monthlyFeeRate`\times 100$ percent of the project will be charged monthly during the development.
\item $`r finalFeeRate`\times 100$ percent of the project will be charged when the project is finished.
\item $`r monthlyRentRate`\times 100$ percent of the total price will be charged monthly for project maintenance.
\end{itemize}

The positive cash flows that the company will obtain during the following $`r t`$ years due to the development of these type of projects will look similar to the following graph:

```{r small projects cash flows graph, fig.align = "center"}
valueSmallProjects$Revenues
```

Project arrivals to the company will look like the following graph:

```{r small projects arrivals graph, fig.align = "center", fig.width = 7, fig.asp = 0.2}
valueSmallProjects$Arrivals
smallProjectsValue <- valueSmallProjects$`Projects PV`
```

Given the previous future cash flows, the present value of the revenues of these projects is worth $\$`r smallProjectsValue`$ MXN.

\section{Large projects}

```{r large projects}
# Princing of the project
projectType="03LargeProjects" # Project type
averagePrice=200000 # Expected price of the project
sdPrice=70000 # Standar deviation of the price of the project
lambda=2 # Expected number of projects developed in a year
# Development time distribution
sop=c(   10,   11,    12,    13,   14,   15,   16)
probs=c(2/37,4/37,15/37,10/37,3/37,2/37,1/37)
# Payment scheme
advanceFeeRate=0.25 # Percentage of the final price that is paid at the begining of the project
monthlyFeeRate=0.5 # Percentage of the final price that is paid during the development of the project
finalFeeRate=0.25 # Percentage of the final price that is paid at the end of the development of the project
monthlyRentRate=0.05 # Percentaje of the price of the project to be charged monthly for project maintenance
  
valueLargeProjects <- getProjectsCashFlows(
  t,
  # Mexican economy
  y, # Annual interest rate
  r, # Inflation rate
  # Project
  projectType, # Project type
  averagePrice, # Expected price of the project
  sdPrice, # Standar deviation of the price of the project
  lambda, # Expected number of projects developed in a year
  # Development time distribution
  sop,
  probs,
  # Payment scheme
  advanceFeeRate, # Percentage of the final price that is paid at the begining of the project
  monthlyFeeRate, # Percentage of the final price that is paid during the development of the project
  finalFeeRate, # Percentage of the final price that is paid at the end of the development of the project
  monthlyRentRate # Percentaje of the price of the project to be charged monthly for project maintenance
)
```

These type of projects will arrive to the company with a ratio of $`r lambda`$ per year and will consider the following assumptions:

\begin{itemize}
\item The price of the project will be $\$`r averagePrice`$ MXN in average with a standar deviation of $\$`r sdPrice`$ MXN and will have the following distribution:

```{r large projects price distribution, fig.align="center", fig.width=4, fig.height=2}
ggplot(data.frame(x = c(0, 2 * averagePrice)), aes(x = x)) + 
  stat_function(fun = dlnorm, args = list(mean = log(averagePrice), sd = 1 / log(sdPrice))) +
  ggtitle("Price density function") +
  labs(x = TeX('$x$'), y = TeX('$f_{Price}(x)$')) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = averagePrice)
```

The vertical line in the graph above represents the average price of the project. 

\item The development time meaured in montsh will have the following discrete distribution:

```{r large projects time distribution, fig.align = "center", fig.width=4, fig.height=2}
vals <- c()
for (i in 1:10000) {
  val <- sampleFromMonthsDistribution(sop = sop, probs = probs)
  vals <- c(vals, val)
}
ggplot(data.frame(vals), aes(x=vals)) + 
  geom_histogram(aes(y = ..count../sum(..count..)), color="black", fill="white") +
  geom_vline(xintercept = mean(vals)) +
  ggtitle("Months probability law") +
  labs(x = TeX('$m (month)$'), y = TeX('$Pr(M=m)$')) +
  theme(plot.title = element_text(hjust = 0.5))
```

The vertical line in the graph above represents the average development time of the project measured in months. 

\item $`r advanceFeeRate`\times 100$ percent of the project will be charged in advance.
\item $`r monthlyFeeRate`\times 100$ percent of the project will be charged monthly during the development.
\item $`r finalFeeRate`\times 100$ percent of the project will be charged when the project is finished.
\item $`r monthlyRentRate`\times 100$ percent of the total price will be charged monthly for project maintenance.
\end{itemize}

The positive cash flows that the company will obtain during the following $`r t`$ years due to the development of these type of projects will look similar to the following graph:

```{r large projects cash flows graph, fig.align = "center"}
valueLargeProjects$Revenues
```

Project arrivals to the company will look like the following graph:

```{r large projects arrivals graph, fig.align = "center", fig.width = 7, fig.asp = 0.2}
valueLargeProjects$Arrivals
largeProjectsValue <- valueLargeProjects$`Projects PV`
```

Given the previous future cash flows, the present value of the revenues of these projects is worth $\$`r largeProjectsValue`$ MXN.

\section{Enterprise projects}

```{r Enterprice projects}
# Princing of the project
projectType="04EnterpriceProjects" # Project type
averagePrice=1600000 # Expected price of the project
sdPrice=200000 # Standar deviation of the price of the project
lambda=1 # Expected number of projects developed in a year
# Development time distribution
sop=c(   13,   14,    15,    16,   17,   18,   19)
probs=c(2/37,4/37,15/37,10/37,3/37,2/37,1/37)
# Payment scheme
advanceFeeRate=0.25 # Percentage of the final price that is paid at the begining of the project
monthlyFeeRate=0.5 # Percentage of the final price that is paid during the development of the project
finalFeeRate=0.25 # Percentage of the final price that is paid at the end of the development of the project
monthlyRentRate=0.05 # Percentaje of the price of the project to be charged monthly for project maintenance
  
valueEnterpriceProjects <- getProjectsCashFlows(
  t,
  # Mexican economy
  y, # Annual interest rate
  r, # Inflation rate
  # Project
  projectType, # Project type
  averagePrice, # Expected price of the project
  sdPrice, # Standar deviation of the price of the project
  lambda, # Expected number of projects developed in a year
  # Development time distribution
  sop,
  probs,
  # Payment scheme
  advanceFeeRate, # Percentage of the final price that is paid at the begining of the project
  monthlyFeeRate, # Percentage of the final price that is paid during the development of the project
  finalFeeRate, # Percentage of the final price that is paid at the end of the development of the project
  monthlyRentRate # Percentaje of the price of the project to be charged monthly for project maintenance
)
```

These type of projects will arrive to the company with a ratio of $`r lambda`$ per year and will consider the following assumptions:

\begin{itemize}
\item The price of the project will be $\$`r averagePrice`$ MXN in average with a standar deviation of $\$`r sdPrice`$ MXN and will have the following distribution:

```{r enterprice projects price distribution, fig.align="center", fig.width=4, fig.height=2}
ggplot(data.frame(x = c(0, 2 * averagePrice)), aes(x = x)) + 
  stat_function(fun = dlnorm, args = list(mean = log(averagePrice), sd = 1 / log(sdPrice))) +
  ggtitle("Price density function") +
  labs(x = TeX('$x$'), y = TeX('$f_{Price}(x)$')) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = averagePrice)
```

The vertical line in the graph above represents the average price of the project. 

\item The development time meaured in montsh will have the following discrete distribution:

```{r enterprice projects time distribution, fig.align = "center", fig.width=4, fig.height=2}
vals <- c()
for (i in 1:10000) {
  val <- sampleFromMonthsDistribution(sop = sop, probs = probs)
  vals <- c(vals, val)
}
ggplot(data.frame(vals), aes(x=vals)) + 
  geom_histogram(aes(y = ..count../sum(..count..)), color="black", fill="white") +
  geom_vline(xintercept = mean(vals)) +
  ggtitle("Months probability law") +
  labs(x = TeX('$m (month)$'), y = TeX('$Pr(M=m)$')) +
  theme(plot.title = element_text(hjust = 0.5))
```

The vertical line in the graph above represents the average development time of the project measured in months. 

\item $`r advanceFeeRate`\times 100$ percent of the project will be charged in advance.
\item $`r monthlyFeeRate`\times 100$ percent of the project will be charged monthly during the development.
\item $`r finalFeeRate`\times 100$ percent of the project will be charged when the project is finished.
\item $`r monthlyRentRate`\times 100$ percent of the total price will be charged monthly for project maintenance.
\end{itemize}

The positive cash flows that the company will obtain during the following $`r t`$ years due to the development of these type of projects will look similar to the following graph:

```{r enterprice projects cash flows graph, fig.align = "center"}
valueEnterpriceProjects$Revenues
```

Project arrivals to the company will look like the following graph:

```{r enterprice projects arrivals graph, fig.align = "center", fig.width = 7, fig.asp = 0.2}
valueEnterpriceProjects$Arrivals
enterpriceProjectsValue <- valueEnterpriceProjects$`Projects PV`
```

Given the previous future cash flows, the present value of the revenues of these projects is worth $\$`r enterpriceProjectsValue`$ MXN.

\section{Inhouse projects}

```{r inhouse projects}
# Project
projectType="05InhouseProjects" # Project type
lambda=1 # Expected number of projects developed in a year
# Development time distribution
sop=c(   10,   11,    12,    13,   14,   15,   16)
probs=c(2/37,4/37,15/37,10/37,3/37,2/37,1/37)
# Payment scheme
averageMonthlyRent=400000 # Project average monthly rent
sdMonthlyRent=100000 # Project monthly rent standar deviation
  
valueInhouseProjects <- getInhouseProjectsCashFlows(
  t, # Lifetime of the company
  # Mexican economy
  y, # Annual interest rate
  r, # Inflation rate
  # Project
  projectType, # Project type
  lambda, # Expected number of projects developed in a year
  # Development time distribution
  sop,
  probs,
  # Payment scheme
  averageMonthlyRent, # Project average monthly rent
  sdMonthlyRent # Project monthly rent standar deviation
)
```

Inhouse projects will arrive to the company with a ratio of $`r lambda`$ per year and will consider the following assumptions:

\begin{itemize}
\item The development time meaured in montsh will have the following discrete distribution:

```{r Iinhouse projects time distribution, fig.align = "center", fig.width=4, fig.height=2}
vals <- c()
for (i in 1:10000) {
  val <- sampleFromMonthsDistribution(sop = sop, probs = probs)
  vals <- c(vals, val)
}
ggplot(data.frame(vals), aes(x=vals)) + 
  geom_histogram(aes(y = ..count../sum(..count..)), color="black", fill="white") +
  geom_vline(xintercept = mean(vals)) +
  ggtitle("Months probability law") +
  labs(x = TeX('$m (month)$'), y = TeX('$Pr(M=m)$')) +
  theme(plot.title = element_text(hjust = 0.5))
```

The vertical line in the graph above represents the average development time of the project measured in months. 

\item The monthly revenue generated by an inhouse project will be $\$`r averageMonthlyRent`$ MXN in average with an standard deviation of $\$`r sdMonthlyRent`$ MXN.
\end{itemize}

The positive cash flows that the company will obtain during the following $`r t`$ years due to inhouse projects development will look similar to the following graph:

```{r inhouse projects cash flows graph, fig.align = "center"}
valueInhouseProjects$Revenues
```

Project arrivals to the company will look like the following graph:

```{r inhouse projects arrivals graph, fig.align = "center", fig.width = 7, fig.asp = 0.2}
valueInhouseProjects$Arrivals
inhouseProjectsValue <- valueInhouseProjects$`Projects PV`
```

Given the previous future cash flows, the present value of inhouse projects development revenues is worth $\$`r inhouseProjectsValue`$ MXN.

\section{Valuation}

```{r net worth}
netWorth <- landigsProjectsValue + smallProjectsValue + largeProjectsValue + enterpriceProjectsValue + inhouseProjectsValue
```

Summing up the net present value of all company's projects the net worth of the company es given by  $\$`r netWorth`$ MXN.